\section{ Board/Bored Games}

From the inside board game industry seems to experienced a renewal; or
at least a huge step was climb the last few decades. Some time ago
there was{\textquotesingle}nt so many publishing company as today, and
most of theses company where connected to toy and children industry
(hasbro, matel, haba), and game designers where totally anonymous(who
know the name of the inventor of monopoly?). ~

Since the 90{\textquotesingle}s this niche market offer hundreds of
publishers, it redefined is own language by defining mechanics and
{\textquotedbl}schools{\textquotedbl}(german-style and american-style)
and best seller game designer begin to apear as the industry grow in
audience.~

These last few years between 800 and 1000 new board game per year are
published, even it could be some add-on sometime, this huge amount of
production create change rythme of a board game life: If you want to
comment,try or know what{\textquotesingle}s going on in this scene you
will have to test at least 2 or 3 games per day before publishers
released the next collection. Few years ago a new and well promoted
game can stand for few month; now if you don{\textquotesingle}t have a
network acess and create attention will need to sucess in few weeks,
even ~days, before everybody forget your box.

Major publisher and authors understand this pretty well and exploit few
expedient to ensure their position. Some prefers funding press of major
press network(Tric-trac is own 49\% per the owner of Asmodee), some
others seem proud to publish game that people already know (Les loups
garoux de Thiercelieux, Time{\textquotesingle}s up) Even this very
small scene seems very friendly the growing concurrence lead to
obliterated news and push publisher to released maintream product,
excluding commercial risk.

Even this communication issue blurred sight for newcomer seeking for
innovative process, the worst is that this collective intent of
mainstream does not seem to work very well... The 10 best selled game
are still antiks like Monopoly, Trivial pursuit, Risk... Common
audience buy what they know. And all this very dynamic production lead
finnaly to a lot of junk, stuck in a niche market and cuted from the
common world. More this fashion of exploiting gamer and geek culture
seem obvious, more the public will have defiance for board game, and
more all the loop of board game production will create junk.

But let{\textquotesingle}s be optimistic and give a final proportion. If
1000 junk game are created this year, and that we can finnaly count on
at least 5 years of analog production since now; we will be able to
play everyday for 15 years from now!

if we begin to think of how we can share rules and material (creative
common, digital reproduction) and process to use new way for playing
(public space, unnacustomed site) we will be able to use all this junk
to create new habit. ~ ~

~

innovation for ~ ~ ~ ~ ~ ~~

{}-1000 game per year

{}-10 best game selled/knowed(people buy what they know)

{}-audience defiance

{}-inovation invisibility
