\section{Daily Life at the Checkpoint}

~

Robots~artists,~killer~drones,~algorithmtic~traders,~chatbot~assistant...~Looks~like~old~visions~of~the~future~are~finally~there~to~colonize~our~present.~Once~silicium~and~petrol~are~processed~into~gadgets~and~machines,~it~doesn{\textquoteright}t~transform~back.~Instead,~it~piles~up~in~our~garages,~filling~our~shelves~and~drawers,~eventually~ending~up~in~some~remote~wasteland.

All~this~accumulated~junk~is~about~to~wake~up.~

It~is~screaming.~

Let~us~be !

\subsection{Holding~the~temporal~rift}

Year~2132.

After~6~years~of~cryonic~unemployment,~you~finally~got~a~job.\newline
The~security~company~X~has~hired~you~to~hold~the~checkpoint~that~controls~travel~through~the~temporal~rift.

A~century~of~wars~between~humans~and~robots~has~left~the~earth~dismembered,~exhausted,~and~overcrowded.~Hybrid~machines~are~now~wandering~in~time-space,~seeking~for~the~days~when~robots~were~funny~home~appliances~living~in~peace.

\subsection{Daily~life~at~a~checkpoint}

Everyday,~unknown~forms~of~life~and~devices~are~queuing~at~the~time~gates,~waiting~for~a~ride~to~the~good~old~times.

Some~are~cool.~Useful,~neat,~practical,~and~friendly.\newline
Some~are~great.~They~could~maybe~save~the~world.\newline
Some~are~evil.~They~will~destroy~or~exhaust~our~planet~in~a~few~seconds.

Anyway,~they~all~have~to~comply~to~the~Time-Travel~Living~Matters~Immigration~Policy~to~cross~the~border.

\begin{itemize}
\item What~is~their~energy~consumption? 
\item Does~their~size~fit~into~our~world? 
\item Are~they~harmful~to~others?~to~humans?~to~dogs? 
\item Are~their~technology~correctly~patented? 
\end{itemize}
Those~are~things~that~you~will~need~to~check.~DNA,~specs,~patents,~built~version,~serial~number...~you~need~to~go~thoroughly~through~all~documents~and~code~available.

\begin{itemize}
\item How~smart~are~they?~ 
\item How~smart~should~they~be ? 
\item Do~we~really~need~them? 
\item Do~we~really~like~them? 
\end{itemize}
You~may~ask~those~questions~to~yourself~.

You~may~allow~them~into~times.\newline
You~may~refuse~them~the~entrance.\newline
Then~you~may~have~to~repair/modify~them~to~let~them~in.

\subsection{Purpose~of~the~Game}

Build~the~most~suitable~and~interesting~objects.

\subsection{Basic~Gameplay}

Player~got~an~object.

Player~talk~to~it~(ask~questions)\newline
//~here,~interface~provides~~to~the~player~a~checklist~of~things~to~ask.

Player~has~to~improve~it~/~change~it~until~it~gets~good~enough~to~pass~the~customs?

At~any~moment,~player~can~refuse~or~let~the~object~in~(accepted/refused)

Once~player~has~decided~object~is~OK,~the~object~is~validated~\newline
(pass~=~WIN~/~destroyed~=~LOSE)

\subsection{Rules}

Player~can~not~refuse~more~than~3~objects~in~a~row.

To~get~into~the~future,~an~object~should~follow~the~Time-Travel~Living~Matters~Immigration~Policy~
