\subsection[What is junk in my own practice ?]{What is junk in
my own practice ?}


As a producer, I didn{\textquoteright}t think I would produce any junk,
cause to me, junk was material stuff. This project made me think of
junk, and realize it{\textquoteright}s much more that that. Maybe all
that meetings I do, dozen of mails every day, printed papers, datas I
produce all the time. What do I do from that ?

~

\subsubsection[Papers]{Papers}
I do a lot of administrative things like hiring people, editing
agreements, payslips, accounting and of course, I have to print all
that and, of course, there is often mistakes and things to change, so I
have to edit them again, and sometimes again AND again{\dots}

So I recycle, it{\textquoteright}s almost an obsession ! Recycling and
throwing that every day out of my office, to clean it up from this
production I can{\textquoteright}t bear to see. Recently, I learnt
throwing every day is a Fen Shui practice and I really understand this
: cause it don{\textquoteright}t throw on you face every morning all
the shit you{\textquoteright}ve produced. It makes you (me) feel more
confortable to this fragile world, those trees. I also keep some to
keep rough papers.

Plus, I{\textquoteright}ve always been recycling since we had the
dustbins for that and could do it, it{\textquoteright}s automatic.

To try to make it right, I{\textquoteright}ve decided to buy only
recycled paper, that I throw after. Recycling the recycled. Get my
practice evolve and think before printing for instance, is the Holy
Grail I try to tend to every day.

~

\subsubsection[Datas]{Datas}
Data is different, well I thought it was different but in fact no, our
datas fill up data centers, billions of billions of bits, countless and
endless informations flowing into boundless data tubes. How much energy
does it require, how many tons of toxic chemical products, plastics ?
Like ogres, they need to be fed, it{\textquoteright}s a system that
requires us to produce datas in order to be fed and digest those
trillions tons of 0 and 1.

I produce data, so much again, editing charts and pages all the time for
every single project, and also a lot of recap charts of course, of
those datas..

This I keep it all, no throwing, you never know right ? So much junk
data but I can be useful one day, kneed, I recycle my own production,
using my datas back, reloading them to adapt them to another new
project. I get them evolve like that and the first one
don{\textquoteright}t really look like the latest I{\textquoteright}ve
done, recycling can give you a solid basis for creating.~

I couldn{\textquoteright}t tell if I have created my first chart or not.
I think I did it for my 1st presentation, it{\textquoteright}s a
creative part I really like, how will I talk of an idea, a concept,
explain it by the rules and also by MY rules, cause only this will make
it unique and will put in it my own print, for which
I{\textquoteright}m known.

And I confess I do recycle the good ideas I see, when I see ;-)

\subsection{Projects}
As a producer again, I read so many projects and initiate much more. How
many comes to the end ? What is junk to others have alreday been good
to me and I know the opposite has been too.

\textit{On going writing...}
