\section{Should}

Using this interface, user can move parameters for each aspect
~
It should feel like level in pipes are moving but no liquid input needed
maybe just move a potentiometer and the liquid effect goes and down
* 1 set of tubes with different levels (potentiometer)
* 1 status indicator
~
glitch?
move buttons?

input water in pipes?~
~
The machine should :

* have a drawer
* be white color
* be in plastic
* have a USB I/O
~
On a table there is demo sequencer (the machine).

Next to the machine, a box of samples is available to test the machine.
~
Visual is generated
~

={\textgreater} apply to object... if we know in advance all the untold
characteristics of an object~ : do we still want it ?
~

People can take a sample and input it into the machine (they may wear
glovers first).
Then , they can use the interface to adjust different parameters : nice
/ bad, dirty / clean, etc.
Once they have setup their objects correctly, they can validate.
The object is added to a display.

\bigskip

People can zoom and interact with the slide.
To place a slide in the slot, people should open a door.~
The start signal should be sent when user close the door.
~
* 1 slot for a prepared slide : 75 mm by 25 mm (3[2033?] by 1[2033?])
* 1 camera (focus and 1 zoom/microscopic camera lens?)
* 1 decoding app~
* 1 barcode scanner (may not be needed as everything will be generated)
* 1 case~ with a door
~
Pour \^etre accept\'e en cabine, votre bagage doit mesurer au maximum 55
x 35 x 25 cm~

* Width : 25 cm

* Height : 31 cm

* Depth : 22 cm

* Weight : 3-4 kg?


\bigskip

When a slide is placed in the scanner slot, it send a signal to start a
new object definition.

~

Scanner may be 1 Raspberry Pi connected to a webcam with a lens

Open Source Dna Sequencer(case looks good!)
~

The installation recreates a futuristic setup where a machine called
{\textquotesingle}The Junkware Sequencer{\textquotesingle} can be used
to twist parameters of living matters basde on text description.~
Object transgenesis through semantic bending
Textual description of objects are generated from patents.~
The visitor can use the machine to visualize and adjust parameters of
its object.

\bigskip

The decoder is a screen where people can monitor the state of their
sample.
It shows activity of the cell.

\bigskip

We should wear lab~white coats and glasses.
