\section{Team}

\subsection{Cl\'ement Renaud - artistic direction}
Cl\'ement Renaud develop experimental initiatives at the crossroad of
art, code, science and technologies. After 6 years in China, he is now
researching about new innovation models worlwide at the LTCI lab of
ParisTech Telecom.
\href{http://clementrenaud.com/}{http://clementrenaud.com}


\subsection{Catherine Lenoble Digital writings}
Catherine Lenoble explores writing in a networked environment. Ubiquity
is the hero of her first novel petitBain, a meta-narrative published in
2010. Since 2012, she proposes creative workshops at the intersection
of collaborative writing \& public space.
\href{http://litteraturing.wordpress.com/}{http://litteraturing.wordpress.com}


\subsection{Julien Maudet Game designer
}Julien Maudet is a game designer and publisher. He founded in 2011
Les~Chiens de l{\textquoteright}Enfer to explore publishing,
collaborative writing and distribution practices of board games in
urban environment (print-on-demand, 3D printing, in situ
creation).
\href{http://dcalk.org/}{http://dcalk.org}

\subsection{Qu Hongyuan Stage designer
}Both fashion and stage designer, Qu Hongyuan works between Shanghai~and
Lyon. She has founded in 2011 the 3rd Hand project to experiment~ways
of upcycling second hand clothes and fabric.
http://quhongyuan.com

\subsection{Lionel Radisson Interactive designer}
Lionel Radisson creates installations where video, objects, languages
and digital writings meet through generative design. His works have
been shown in international exhibitions (Saint-\'Etienne Design
Biennale, Bruxelles Nuit Blanche, CMoDA...)
\href{http://makio135com/}{http://makio135com}


\bigskip

\subsection{Sophia Lin Curator China}
Chinese-canadian living in Shanghai, Sophia Lin has founded the Make+
programe where artists, designers, academics and technologists from all
over the world work together to develop projets artistic and
experimental tech projects.~
\href{http://makeplus.org/}{http://makeplus.org}

\subsection{Merryl Messaoudi Production}
Somewhere between film set, opera stages and music festivals, Merryl
Messaoudi manage production development of projects and initiatives
supporting hybrid and innovative writings. 
\href{http://www.crossedlab.org/}{http://www.crossedlab.org}
\endinput
